Output Summary

### 2023-05-10 03-post-process/output-plots-children/06-length-based-survival.Rmd
Tiny plotting bug fix

  # expected relationship
  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tran_cols["model"])
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = tran_cols["model"], lwd = 2)

>>>>

  # expected relationship
  polygon(c(L_Mb_seq, rev(L_Mb_seq)), c(pred_phi_Mb_Ma_lwr, rev(pred_phi_Mb_Ma_upr)), border = NA, col = tran_cols["model"])
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = main_cols["model"], lwd = 2)
